---
title: "RcppAlphahull installation and first test"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Installation

Up to now is possible to install this package easily on Linux and in order to do that I suggest to follow the following procedure:

* install R development package with the command `sudo apt-get install r-base-dev` in the command line,;
* open R with the command `R` in command line or, if you have installed [Rstudio desktop version](https://www.rstudio.com/products/rstudio/download/#download), open it;
* install the library `devtools` with the command `install.packages('devtools')`, this may take a while depending on the tools that have been already installed on your R version if you already had it;
* unlickily the devtools command  `install_github` apparently does not install packages dependencies, so I suggest to install the package  `alpahull` directly with the command `install.packages('alphahull')`;
* install ```RcppAlphahull``` using the command `devtools::install_github("https://github.com/federicoairoldi/ProgettoPACS", subdir = "RcppAlphahull")`.

If no error occurs the installation has worked fine.

## A first example test

After the installation we can run the following code to perform a small simple test. The plot shows the α-convex hull in red, the α-shape in blue and the Voronoi diagram in black.

```{r first test}
library(RcppAlphahull) # loading the package
n = 50
set.seed(1)
x = runif(n) # sampling the points
y = runif(n)
alpha = 0.1

ahull.example = ahull(x,y,alpha)

plot(ahull.example, asp = 1, do.shape = T, wlines = "vor", col = c("red","blue","black","black","black","black"), xlab = "", ylab = "", main = "Your 1st test with RcppAlphahull")
```

## How can you be sure I'm not cheating?

Since the function that performs the computation have the same name in the two packages one can think that I just embedded the  `alpahull` code in a sort of wrapper package. If you want to test such eventuality you can execute the code below.

```{r performances}
n = 500
set.seed(1)
x = runif(n,0,10) # sampling the points
y = runif(n,0,10)
alpha = 0.5
  
system.time(RcppAlphahull::ahull(x,y,alpha))
system.time(alphahull::ahull(x,y,alpha))
```

By runnning this code one should see that the `RcppAlpahull` function performs more faster than the `alpahull` one. The result of the α-convex hull computation is shown in the following plot.

```{r plot, echo=FALSE}
n = 500
set.seed(1)
x = runif(n,0,10) # sampling the points
y = runif(n,0,10)
alpha = 0.5
plot(RcppAlphahull::ahull(x,y,alpha), asp = 1, col = c("red","blue","black","black","black","black"), xlab = "", ylab = "", main = expression(paste(alpha,"-convex hull for a set of 1000 points")))
```
